---
title: "ETH"
output: html_document
date: "2022-11-29"
---

## Introduction
The purpose of this project is to predict Etherums price through NFT market performance and other predictors. The project uses supervised model and consists of two part: 1.explore relationship between variables and performing necessary adjustment 2.fit model and forecast

```{r}
library(janitor)
library(corrplot)
library(tidymodels)
library(tidyverse)
library(ISLR)
library(rpart.plot)
library(vip)
library(janitor)
library(randomForest)
library(xgboost)
library(ranger)
tidymodels_prefer(quiet = TRUE)
library(conflicted)
library(discrim)
library(poissonreg)
library(corrr)
tidymodels_prefer()
suppressMessages(library(tidyquant))
library(ggplot2)
library(fitdistrplus)
library(reshape2)
library(patchwork)
library(parallel)
library(lsr)
library(tidyquant)
library(caret)
library(leaps)
```

```{r}
eth <- read.csv("/Users/williamwang/Desktop/Wilw-131HW/Dataset/ETH Data.csv")
USD <- tq_get("DX-Y.NYB", get = "stock.price", from = " 2021-11-30", to = "2022-11-25")
Riot <- tq_get("RIOT", get = "stock.price", from = " 2021-11-30", to = "2022-11-25")
Gold <- tq_get("GC=F", get = "stock.price", from = " 2021-11-30", to = "2022-11-25")
Nasdaq <- tq_get("NQ=F", get = "stock.price", from = " 2021-11-30", to = "2022-11-25")
Treasureyield <- tq_get("^TNX", get = "stock.price", from = " 2021-11-30", to = "2022-11-25")
```

```{r}
USD$date <- as.character(USD$date)
Riot$date <- as.character(Riot$date)
Gold$date <- as.character(Gold$date)
Nasdaq$date <- as.character(Nasdaq$date)
Treasureyield$date <- as.character(Treasureyield$date)
```



```{r}
match(Riot$date,Gold$date)
Gold$close[match(Riot$date,Gold$date)]
Riot$Gold_close=Gold$close[match(Riot$date,Gold$date)]
na.omit(Riot)
Dataset <- Riot
```




```{r}
Dataset <- Dataset[ , c("date","close", "Gold_close")]
Dataset <- rename(Dataset, Riot_close=close)

```

```{r}
match(Dataset$date,USD$date)
USD$close[match(Dataset$date,USD$date)]
Dataset$USD_close=USD$close[match(Dataset$date,USD$date)]
na.omit(Dataset)
```

```{r}
match(Dataset$date,Nasdaq$date)
Nasdaq$close[match(Dataset$date,Nasdaq$date)]
Dataset$Nasdaq_close=Nasdaq$close[match(Dataset$date,Nasdaq$date)]
na.omit(Dataset)
Dataset
```

```{r}
match(Dataset$date,Treasureyield$date)
Treasureyield$close[match(Dataset$date,Treasureyield$date)]
Dataset$Treasureyield_close=Treasureyield$close[match(Dataset$date,Treasureyield$date)]
na.omit(Dataset)
Dataset
```

```{r}
xxxx <- match(Dataset$date,eth$Date)
list1 <- na.omit(xxxx)
eth <- eth[c(list1),]
```

```{r}
Dataset <- rename(Dataset, Date = date)
Data <- merge(Dataset, eth, by = "Date")
Data
```
##Explorarotory Data Analysis

```{r}
ggplot(Data,aes(x=Log.return.ETH))+
  geom_histogram(bins = 50, color = "red")+
  labs(title = "Histogram of ETH price at close") +
  theme(legend.position = "none")
```

```{r}
cor_Data <- Data %>%
  select_if(is.numeric) %>%
  lsr::correlate()

#rplot(cor_df$correlation)

corrplot(cor_Data$correlation)
```


```{r}
Data = subset(Data, select = -c(Log.return.ETH,Nasdaq_close,USD_close,ETH_Volume) )
Data
```


```{r}
cor_Data <- Data %>%
  select_if(is.numeric) %>%
  lsr::correlate()

#rplot(cor_df$correlation)

corrplot(cor_Data$correlation)
```


```{r}
plot.ts(Data$ETH_Close, main="ETH price Regression")
fit <- lm(Data$ETH_Close ~ as.numeric(1:length(Data$ETH_Close)))
abline(fit, col="red")
abline(h=mean(Data$ETH_Close), col="blue")
```

```{r}
P1 <- Data %>%
  ggplot(aes(x=Riot_close, y=ETH_Close)) + 
  geom_point(alpha = 0.2) + 
  labs(title = 'Riot Price vs ETH Price') +
  geom_smooth(method = 'lm', formula = 'y ~ x') +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))
P2 <- Data %>%
  ggplot(aes(x=Gold_close, y=ETH_Close)) + 
  geom_point(alpha = 0.2) + 
  labs(title = 'Gold Price vs ETH Price') +
  geom_smooth(method = 'lm', formula = 'y ~ x') +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))
P3 <- Data %>%
  ggplot(aes(x=Treasureyield_close, y=ETH_Close)) + 
  geom_point(alpha = 0.2) + 
  labs(title = 'Treasureyield Price vs ETH Price') +
  geom_smooth(method = 'lm', formula = 'y ~ x') +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))
P4 <- Data %>%
  ggplot(aes(x=Number.of.sales.in.all.segments, y=ETH_Close)) + 
  geom_point(alpha = 0.2) + 
  labs(title = 'Number of NFT sales vs ETH Price') +
  geom_smooth(method = 'lm', formula = 'y ~ x') +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))
P4 <- Data %>%
  ggplot(aes(x=Active.market.wallets.in.all.segments, y=ETH_Close)) + 
  geom_point(alpha = 0.2) + 
  labs(title = 'Number of active wallets in NFT market vs ETH Price') +
  geom_smooth(method = 'lm', formula = 'y ~ x') +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))
P5 <- Data %>%
  ggplot(aes(x=Average.USD, y=ETH_Close)) + 
  geom_point(alpha = 0.2) + 
  labs(title = 'Average sale price(USD) in NFT market vs ETH Price') +
  geom_smooth(method = 'lm', formula = 'y ~ x') +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))
P6 <- Data %>%
  ggplot(aes(x=Sales.USD, y=ETH_Close)) + 
  geom_point(alpha = 0.2) + 
  labs(title = 'Total sales (USD) in NFT market vs ETH Price') +
  geom_smooth(method = 'lm', formula = 'y ~ x') +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))
P1+P2+P3+P4+P5+P6
```


## EDA Summary
From the graphs showned above, we can see that the simple linear regression does not fit the data very well.

```{r}
set.seed(300)
Data_Train <- Data %>%
  initial_split(prop = 0.8) #it roughly seperates the data before and after year 2020
eth_train <- training(Data_Train)
eth_test <- testing(Data_Train)
```

## recipe creation& K-fold
```{r}
eth_recipe <- recipe(ETH_Close ~ Riot_close + Gold_close + Treasureyield_close+
                      Sales.USD + Number.of.sales.in.all.segments + Active.market.wallets.in.all.segments + Average.USD,
                    data = Data) %>%
  step_dummy(all_nominal_predictors()) %>%
  step_normalize(all_predictors()) %>%
  step_novel(all_nominal_predictors()) %>%
  step_zv(all_nominal_predictors())
               
eth_folds <- vfold_cv(eth_train, v = 10, repeats = 5)
```

## Ridge Regression
```{r}
#set up model
ridge_spec <- linear_reg(penalty = tune(), mixture = 0) %>%
  set_mode("regression") %>%
  set_engine("glmnet")

#set up workflow
ridge_workflow <- workflow() %>%
  add_recipe(eth_recipe) %>%
  add_model(ridge_spec)

# Create a regular grid
penalty_grid <- grid_regular(penalty(range = c(-5, 5), trans = log10_trans()), levels = 20)


# Fit the models to the folded data using tune_grid().
tune_res <- tune_grid(
  ridge_workflow,
  resamples = eth_folds,
  grid = penalty_grid
)



# use autoplot() on the results
autoplot(tune_res)
```

##Collect Ridge Metric
```{r}
Ridge_RMSE <- collect_metrics(tune_res) %>%
  dplyr::select(.metric, mean, std_err)
Ridge_RMSE <-  Ridge_RMSE[c(1,2),]
```

```{r}
best_penalty <- select_best(tune_res, metric = "rsq")
best_penalty
```

```{r}
ridge_final <- finalize_workflow(ridge_workflow, best_penalty)
ridge_final_fit <- fit(ridge_final, data = eth_train)

Ridge_Prediction <- predict(ridge_final_fit, 
                            new_data = eth_test %>% 
                              dplyr::select(-`ETH_Close`))
Ridge_Prediction <- bind_cols(Ridge_Prediction, 
                              eth_test %>% 
                                dplyr::select(`ETH_Close`))

Ridge_Graph <- Ridge_Prediction %>%
  ggplot(aes(x=.pred, y=`ETH_Close`)) + 
  geom_point(alpha = 1) + 
  geom_abline(lty = 2) + 
  theme_bw() + 
  coord_obs_pred()

Ridge_Accuracy <- augment(ridge_final_fit, new_data = eth_test) %>%
  rsq(truth = `ETH_Close`, estimate = .pred)
```

##Lasso Regression
```{r}
lasso_spec <-
  linear_reg(penalty = tune(), mixture = 1) %>%
  set_mode("regression") %>%
  set_engine("glmnet")


lasso_workflow <- workflow() %>%
  add_recipe(eth_recipe) %>%
  add_model(lasso_spec)



tune_res_lasso <- tune_grid(
  lasso_workflow,
  resamples = eth_folds,
  grid = penalty_grid
)


autoplot(tune_res_lasso)
```


```{r}
Lasso_RMSE <- collect_metrics(tune_res_lasso) %>%
  dplyr::select(.metric, mean, std_err) %>%
  head(2)#?
```

```{r}
best_penalty_lasso <- select_best(tune_res_lasso, metric = "rsq")
lasso_final <- finalize_workflow(lasso_workflow, best_penalty_lasso)

lasso_final_fit <- fit(lasso_final, data = eth_train)
Lasso_Prediction <- predict(lasso_final_fit, new_data = eth_test %>% 
                              dplyr::select(-`ETH_Close`))
Lasso_Prediction <- bind_cols(Lasso_Prediction, eth_test %>% 
                                dplyr::select(`ETH_Close`))
Lasso_Graph <- Lasso_Prediction %>%
  ggplot(aes(x=.pred, y=`ETH_Close`)) + 
  geom_point(alpha=1) + 
  geom_abline(lty = 2) + 
  theme_bw() + 
  coord_obs_pred()
Lasso_Accuracy <- augment(lasso_final_fit, new_data = eth_test) %>%
  rsq(truth = `ETH_Close`, estimate = .pred)
```

##KNN
```{r}
KNN_spec <-nearest_neighbor() %>%
  set_mode("regression") %>%
  set_engine("kknn") %>% 
  set_args(neighbors = tune(),
           weight_func = tune(),
           dist_power = tune())

translate(KNN_spec)
```


```{r}
KNN_workflow <- workflow() %>%
  add_recipe(eth_recipe) %>%
  add_model(KNN_spec)


knn1_res <- tune_grid(
  KNN_workflow,
  resamples = eth_folds,
  # control = tune::control_resamples(save_pred = TRUE)
)

autoplot(knn1_res)
```

```{r}
KNN_RMSE <- collect_metrics(knn1_res) %>% 
  dplyr::select(.metric, mean, std_err) %>% 
  head()


best_KNN_final <- select_best(knn1_res,metric = "rsq")
best_KNN_final_model <- finalize_workflow(KNN_workflow, best_KNN_final)

best_KNN_final_model_fit <- fit(best_KNN_final_model, data = eth_train)
KNN_Prediction <- predict(best_KNN_final_model_fit, 
                            new_data = eth_test %>% 
                              dplyr::select(-`ETH_Close`))
KNN_Prediction <- bind_cols(KNN_Prediction, 
                              gld_test %>% 
                              dplyr::select(`ETH_Close`))
KNN_Graph <- KNN_Prediction %>%
  ggplot(aes(x=.pred, y=`eth_close`)) + 
  geom_point(alpha=1) + 
  geom_abline(lty = 2) + 
  theme_bw() + 
  coord_obs_pred()
Boost_Accuracy <- augment(best_KNN_final_model_fit, new_data = eth_test) %>%
  rsq(truth = `ETH_Close`, estimate = .pred)
```

##Booseted Model
```{r}
boost_spec <- boost_tree() %>%
  set_engine("xgboost") %>%
  set_mode("regression")

boost_wf <- workflow() %>%
  add_model(boost_spec %>%
  set_args(trees = tune())) %>%
  add_recipe(eth_recipe)

boost_grid <- grid_regular(trees(range = c(10, 100)), levels = 10)

boost_tune_res <- tune_grid(
  boost_wf,
  resamples = eth_folds,
  grid = boost_grid,
)
autoplot(boost_tune_res)
```

```{r}
Boost_RMSE <- collect_metrics(boost_tune_res) %>% 
  dplyr::select(.metric, mean, std_err) %>%
  head()
```

```{r}
best_boost_final <- select_best(boost_tune_res,metric = "rsq")
best_boost_final_model <- finalize_workflow(boost_wf, best_boost_final)

best_boost_final_model_fit <- fit(best_boost_final_model, data = eth_train)
Boost_Prediction <- predict(best_boost_final_model_fit, 
                            new_data = eth_test %>% 
                              dplyr::select(-`ETH_Close`))
Boost_Prediction <- bind_cols(Boost_Prediction, 
                              eth_test %>% 
                              dplyr::select(`ETH_Close`))
Boost_Graph <- Boost_Prediction %>%
  ggplot(aes(x=.pred, y=`ETH_Close`)) + 
  geom_point(alpha=1) + 
  geom_abline(lty = 2) + 
  theme_bw() + 
  coord_obs_pred()
Boost_Accuracy <- augment(best_boost_final_model_fit, new_data = eth_test) %>%
  rsq(truth = `ETH_Close`, estimate = .pred)
```

##Decision Tree
```{r}
tree_spec <-decision_tree() %>%
  set_engine("rpart")
class_tree_spec <- tree_spec %>%
  set_mode("regression")
  
class_tree_wf <- workflow() %>%
  add_model(class_tree_spec %>% 
            set_args(cost_complexity = tune())) %>%
  add_recipe(eth_recipe)

param_grid <- grid_regular(cost_complexity(range = c(-5, 0)), levels = 10)
tune_res_tree <- tune_grid(
  class_tree_wf,
  resamples = eth_folds,
  grid = param_grid,
)
autoplot(tune_res_tree)
```

```{r}
Tree_RMSE <- collect_metrics(tune_res_tree) %>%
  dplyr::select(.metric, mean, std_err) %>%
  head(2)
```

```{r}
library(rpart.plot)
best_complexity <- select_best(tune_res_tree, "rsq")
class_tree_final <- finalize_workflow(class_tree_wf, best_complexity)
class_tree_final_fit <- fit(class_tree_final, data = eth_train)
class_tree_final_fit %>%
  extract_fit_engine() %>%
  rpart.plot()
```

```{r}
Tree_Prediction <- predict(class_tree_final_fit, 
                           new_data = eth_test %>% 
                             dplyr::select(-`ETH_Close`))
Tree_Prediction <- bind_cols(Tree_Prediction, 
                             gld_test %>% 
                               dplyr::select(`ETH_Close`))
Tree_Graph <- Tree_Prediction %>%
  ggplot(aes(x=.pred, y=`ETH_Close`)) + 
  geom_point(alpha=1) + 
  geom_abline(lty = 2) + 
  theme_bw() + 
  coord_obs_pred()
Tree_Accuracy <- augment(class_tree_final_fit, new_data = eth_test) %>%
  rsq(truth = `ETH_Close`, estimate = .pred)
```

##Model Comparison
```{r}
library(ggpubr)
figure <- ggarrange(Ridge_Graph, Lasso_Graph, Boost_Graph,Tree_Graph,KNN_Graph,
                    labels = c("Ridge", "Lasso", "Boost","Tree","KNN"),
                    ncol = 3, nrow = 3)
figure
```

Analysis:

##RMSE & RSQ in Training Set
```{r}
head(Ridge_RMSE)
```

```{r}
head(Lasso_RMSE)
```

```{r}
head(Boost_RMSE, 2)
```

```{r}
head(Tree_RMSE, 2)
```

```{r}
head(KNN_RMSE)
```

Analysis:

##R-Squared of Testing Set
```{r}
rsq_comparisons <- bind_rows(Ridge_Accuracy, Lasso_Accuracy, Boost_Accuracy, Tree_Accuracy) %>% 
  tibble() %>% 
  mutate(model = c("Ridge", "Lasso", "Boost", "Tree")) %>% 
  dplyr::select(model, .estimate) %>%
  arrange(.estimate)
rsq_comparisons
```

Analysis:

##Conclusion














